Scattering of massless particles: scalars, gluons and gravitons

### 2024-07-03 test/main.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usepackage{tikz}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[CHY formula]{Scattering of massless particles: scalars, gluons and gravitons}
\subtitle{Freddy Cachazo, Song He, Ellis Ye Yuan}
\author{Su Yingze}
\institute{Nagoya University}
\date[7 23rd 2024]{July 23rd 2024} 
\begin{document}
\frame{\titlepage}

@@

\end{frame}
\begin{frame}
    Likewise the decomposition in the first section, it is more usually to write the amplitudes in terms of colore basis
    \begin{equation*}
        \boxed{\mathbf{c}_\alpha\equiv\sum_{\mathsf{c}_1,...,\mathsf{c}_{n-3}}f_{\mathsf{a}_1\mathsf{a}_{\alpha(2)}\mathsf{c}_1}\cdots f_{\mathsf{c}_{n-3}\mathsf{a}_{\alpha(n-1)}\mathsf{a}_n}}
    \end{equation*}
    where $\alpha \in S_{n-2}$. The amplitude is 
    \begin{equation*}
        \mathcal{M}_n^{(0)}=\sum_{\alpha,\beta\in S_{n-2}}\mathbf{c_\alpha}\tilde{\mathbf{c_\beta}}m_{n}^{(0)}(\alpha|\beta)
    \end{equation*}
\end{frame}
\begin{frame}
    \frametitle{Examples}
    \begin{itemize}
        \item The simplest example is the 3 point case
        \begin{equation*}
            \mathcal{M}_3^{(0)}(1^{aa^\prime,bb^\prime,cc^\prime})=(\sigma_{12}\sigma_{23}\sigma_{31})^2\frac{f_{abc}f_{a^\prime b^\prime c^\prime}}{(\sigma_{12}\sigma_{23}\sigma_{31})^2}=f_{abc}f_{a^\prime b^\prime c^\prime}
        \end{equation*}
        It actually gives the correct answer.
        \item The 4 point case is a little complex. Solving the scattering equations with $\sigma_1=0,\sigma_2=1,\sigma_3=\infty$ gives $\sigma_4=-s_{23}/s_{12}$. Define
        $s_{12}=s$, $s_{23}=t$, $s_{13}=u$, the color factors are 
        \begin{equation*}
            \mathbf{c_s}=\sum_bf_{a_1a_2b}f_{ba_3a_4},\mathbf{c_t}=\sum_bf_{a_1a_4b}f_{ba_3a_2},\mathbf{c_u}=\sum_bf_{a_1a_3b}f_{ba_2a_4}
        \end{equation*}
        Denoting the ordering $(1324)$ as $P$ and comuputing $\det{'}\Phi=\frac{s^2}{t}/(\sigma_{12}\sigma_{23}^2\sigma_{31}\sigma_{34}\sigma_{42})$, one gets
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{align*}
        \!\!\!\!\mathcal{M}_4^{(0)}&=\mathbf{c_s}\tilde{\mathbf{c_s}}m_4^{(0)}(I;I)+\mathbf{c_s}\tilde{\mathbf{c_u}}m_4^{(0)}(I;P)+\mathbf{c_u}\tilde{\mathbf{c_s}}m_4^{(0)}(P;I)+\mathbf{c_u}\tilde{\mathbf{c_u}}m_4^{(0)}(P;P)\\
        &=\mathbf{c_s}\tilde{\mathbf{c_s}}\frac{u}{st}+(\mathbf{c_s}\tilde{\mathbf{c_u}}+\mathbf{c_u}\tilde{\mathbf{c_s}})\frac{1}{t}+\mathbf{c_u}\tilde{\mathbf{c_u}}\frac{s}{ut}\\
        &=-\frac{\mathbf{c_s}\tilde{\mathbf{c_s}}}{s}-\frac{\mathbf{c_t}\tilde{\mathbf{c_t}}}{t}-\frac{\mathbf{c_u}\tilde{\mathbf{c_u}}}{u}
    \end{align*}
    \quad \quad as expected for a color-dressed cubic theory.
    \begin{itemize}
        \item For the five point, I just give the results of some double partial amplitudes.
        Denoting the orderings as $I=P_0$, $(13245)=P_1$, $(12435)=P_2$, $(14325)=P_3$, $(13425)=P_4$, $(14235)=P_5$
        \begin{equation*}
            \begin{aligned}&m_5^{(0)}(I|I)=\frac{1}{s_{12}s_{34}}+\frac{1}{s_{23}s_{45}}+\frac{1}{s_{34}s_{51}}+\frac{1}{s_{45}s_{12}}+\frac{1}{s_{51}s_{23}},\\&m_5^{(0)}(I|P_1)=-\frac{1}{s_{23}}\left(\frac{1}{s_{45}}+\frac{1}{s_{12}}\right),\quad
                m_5^{(0)}(I|P_2)=-\frac{1}{s_{34}}\left(\frac{1}{s_{51}}+\frac{1}{s_{12}}\right).\end{aligned}
        \end{equation*}
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{align*}
        &m_5^{(0)}(I|P_3)=-\frac{1}{s_{51}}\left(\frac{1}{s_{23}}+\frac{1}{s_{34}}\right),\quad  m_5^{(0)}(I|P_2)=-\frac{1}{s_{34}s_{51}},\\
        &m_5^{(0)}(I|P_5)=0
    \end{align*}
\end{frame}

\end{document}

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usepackage{tikz}
\usepackage{svg}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[CHY formula]{Scattering of massless particles: scalars, gluons and gravitons}
\subtitle{Freddy Cachazo, Song He, Ellis Ye Yuan}
\author{Su Yingze}
\institute{Nagoya University}
\date[7 23rd 2024]{July 23rd 2024} 
\begin{document}
\frame{\titlepage}

@@

\end{frame}
\begin{frame}
    Likewise the decomposition in the first section, it is more usually to write the amplitudes in terms of colore basis
    \begin{equation*}
        \boxed{\mathbf{c}_\alpha\equiv\sum_{\mathsf{c}_1,...,\mathsf{c}_{n-3}}f_{\mathsf{a}_1\mathsf{a}_{\alpha(2)}\mathsf{c}_1}\cdots f_{\mathsf{c}_{n-3}\mathsf{a}_{\alpha(n-1)}\mathsf{a}_n}}
    \end{equation*}
    where $\alpha \in S_{n-2}$. The amplitude is 
    \begin{equation*}
        \mathcal{M}_n^{(0)}=\sum_{\alpha,\beta\in S_{n-2}}\mathbf{c_\alpha}\tilde{\mathbf{c_\beta}}m_{n}^{(0)}(\alpha|\beta)
    \end{equation*}
\end{frame}
\begin{frame}
    \frametitle{Examples}
    \begin{itemize}
        \item The simplest example is the 3 point case
        \begin{equation*}
            \mathcal{M}_3^{(0)}(1^{aa^\prime,bb^\prime,cc^\prime})=(\sigma_{12}\sigma_{23}\sigma_{31})^2\frac{f_{abc}f_{a^\prime b^\prime c^\prime}}{(\sigma_{12}\sigma_{23}\sigma_{31})^2}=f_{abc}f_{a^\prime b^\prime c^\prime}
        \end{equation*}
        It actually gives the correct answer.
        \item The 4 point case is a little complex. Solving the scattering equations with $\sigma_1=0,\sigma_2=1,\sigma_3=\infty$ gives $\sigma_4=-s_{23}/s_{12}$. Define
        $s_{12}=s$, $s_{23}=t$, $s_{13}=u$, the color factors are 
        \begin{equation*}
            \mathbf{c_s}=\sum_bf_{a_1a_2b}f_{ba_3a_4},\mathbf{c_t}=\sum_bf_{a_1a_4b}f_{ba_3a_2},\mathbf{c_u}=\sum_bf_{a_1a_3b}f_{ba_2a_4}
        \end{equation*}
        Denoting the ordering $(1324)$ as $P$ and comuputing $\det{'}\Phi=\frac{s^2}{t}/(\sigma_{12}\sigma_{23}^2\sigma_{31}\sigma_{34}\sigma_{42})$, one gets
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{align*}
        \!\!\!\!\mathcal{M}_4^{(0)}&=\mathbf{c_s}\tilde{\mathbf{c_s}}m_4^{(0)}(I;I)+\mathbf{c_s}\tilde{\mathbf{c_u}}m_4^{(0)}(I;P)+\mathbf{c_u}\tilde{\mathbf{c_s}}m_4^{(0)}(P;I)+\mathbf{c_u}\tilde{\mathbf{c_u}}m_4^{(0)}(P;P)\\
        &=\mathbf{c_s}\tilde{\mathbf{c_s}}\frac{u}{st}+(\mathbf{c_s}\tilde{\mathbf{c_u}}+\mathbf{c_u}\tilde{\mathbf{c_s}})\frac{1}{t}+\mathbf{c_u}\tilde{\mathbf{c_u}}\frac{s}{ut}\\
        &=-\frac{\mathbf{c_s}\tilde{\mathbf{c_s}}}{s}-\frac{\mathbf{c_t}\tilde{\mathbf{c_t}}}{t}-\frac{\mathbf{c_u}\tilde{\mathbf{c_u}}}{u}
    \end{align*}
    \quad \quad as expected for a color-dressed cubic theory.
    \begin{itemize}
        \item For the five point, I just give the results of some double partial amplitudes.
        Denoting the orderings as $I=P_0$, $(13245)=P_1$, $(12435)=P_2$, $(14325)=P_3$, $(13425)=P_4$, $(14235)=P_5$
        \begin{equation*}
            \begin{aligned}&m_5^{(0)}(I|I)=\frac{1}{s_{12}s_{34}}+\frac{1}{s_{23}s_{45}}+\frac{1}{s_{34}s_{51}}+\frac{1}{s_{45}s_{12}}+\frac{1}{s_{51}s_{23}},\\&m_5^{(0)}(I|P_1)=-\frac{1}{s_{23}}\left(\frac{1}{s_{45}}+\frac{1}{s_{12}}\right),\quad
                m_5^{(0)}(I|P_2)=-\frac{1}{s_{34}}\left(\frac{1}{s_{51}}+\frac{1}{s_{12}}\right).\end{aligned}
        \end{equation*}
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{align*}
        &m_5^{(0)}(I|P_3)=-\frac{1}{s_{51}}\left(\frac{1}{s_{23}}+\frac{1}{s_{34}}\right),\quad  m_5^{(0)}(I|P_4)=-\frac{1}{s_{34}s_{51}},\\
        &m_5^{(0)}(I|P_5)=0
    \end{align*}
    From there examples, it is easy to see that when both permutations in $m_n^{(0)}(\alpha|\beta)$ are the same, then the answer is a sum over all color-orded
    trivalent diagrams; When the two permutations are different, it gives a subset of terms of $m_n^{(0)}(\alpha|\alpha)$. 
    \\ \hspace*{\fill}\\
    More explictly,

    \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

    \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
    %uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

    %Straight Lines [id:da8455657796938298] 
    \draw    (179.5,110) -- (212.5,142) ;
    %Straight Lines [id:da5324594211620186] 
    \draw    (212.5,142) -- (182.5,170) ;
    %Straight Lines [id:da4643902351443361] 
    \draw    (212.5,142) -- (254.5,142) ;
    %Straight Lines [id:da8904360433186445] 
    \draw    (280.5,111) -- (254.5,142) ;
    %Straight Lines [id:da18000644921445508] 
    \draw    (254.5,142) -- (281.5,171) ;
    %Straight Lines [id:da29602344087941934] 
    \draw    (320.5,109) -- (353.5,141) ;
    %Straight Lines [id:da9975053882839713] 
    \draw    (353.5,141) -- (323.5,169) ;
    %Straight Lines [id:da5157442319090852] 
    \draw    (353.5,141) -- (395.5,141) ;
    %Straight Lines [id:da049884375007126946] 
    \draw    (421.5,110) -- (395.5,141) ;
    %Straight Lines [id:da9299487354359295] 
    \draw    (395.5,141) -- (422.5,170) ;

    % Text Node
    \draw (111,135.4) node [anchor=north west][inner sep=0.75pt]    {$m_{4}^{(0)}(I,I) =$};
    % Text Node
    \draw (184.5,173) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
    % Text Node
    \draw (184.5,94) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
    % Text Node
    \draw (264.5,94) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
    % Text Node
    \draw (263.5,172) node [anchor=north west][inner sep=0.75pt]   [align=left] {4};
    % Text Node
    \draw (298,133.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
    % Text Node
    \draw (325.5,172) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
    % Text Node
    \draw (325.5,93) node [anchor=north west][inner sep=0.75pt]   [align=left] {4};
    % Text Node
    \draw (405.5,93) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
    % Text Node
    \draw (404.5,171) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};

    \end{tikzpicture}

\end{frame}
\begin{frame}
    Similarly,

    \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

    \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
    %uncomment if require: \path (0,350); %set diagram left start at 0, and has height of 350

    %Straight Lines [id:da8963901965951664] 
    \draw    (84,71) -- (108,93) ;
    %Straight Lines [id:da07470927432540231] 
    \draw    (108,93) -- (136,93) ;
    %Straight Lines [id:da12245379377221366] 
    \draw    (108,93) -- (85,111) ;
    %Straight Lines [id:da6511432990080723] 
    \draw    (136,93) -- (161,114) ;
    %Straight Lines [id:da1430135957918477] 
    \draw    (157,71) -- (136,93) ;
    %Straight Lines [id:da8765002291973463] 
    \draw    (157,71) -- (158,47) ;
    %Straight Lines [id:da9623971067643409] 
    \draw    (157,71) -- (178,87) ;
    %Straight Lines [id:da5561877649988292] 
    \draw    (214,70) -- (238,92) ;
    %Straight Lines [id:da44100018812085007] 
    \draw    (238,92) -- (266,92) ;
    %Straight Lines [id:da05824517478761182] 
    \draw    (238,92) -- (215,110) ;
    %Straight Lines [id:da35334338456014613] 
    \draw    (266,92) -- (291,113) ;
    %Straight Lines [id:da9313767826880515] 
    \draw    (287,70) -- (266,92) ;
    %Straight Lines [id:da696534040519218] 
    \draw    (287,70) -- (288,46) ;
    %Straight Lines [id:da5526828548209644] 
    \draw    (287,70) -- (308,86) ;
    %Straight Lines [id:da19124382298581288] 
    \draw    (359,64) -- (383,86) ;
    %Straight Lines [id:da5237814153432139] 
    \draw    (383,86) -- (411,86) ;
    %Straight Lines [id:da7974585866426673] 
    \draw    (383,86) -- (360,104) ;
    %Straight Lines [id:da46316924534551385] 
    \draw    (411,86) -- (436,107) ;
    %Straight Lines [id:da37617479030606993] 
    \draw    (432,64) -- (411,86) ;
    %Straight Lines [id:da9834219129393018] 
    \draw    (432,64) -- (433,40) ;
    %Straight Lines [id:da7117622111604034] 
    \draw    (432,64) -- (453,80) ;
    %Straight Lines [id:da8760088009181417] 
    \draw    (82,171) -- (106,193) ;
    %Straight Lines [id:da7078786925271212] 
    \draw    (106,193) -- (134,193) ;
    %Straight Lines [id:da5389180018159456] 
    \draw    (106,193) -- (83,211) ;
    %Straight Lines [id:da26578622720899636] 
    \draw    (134,193) -- (159,214) ;
    %Straight Lines [id:da5989066756692625] 
    \draw    (155,171) -- (134,193) ;
    %Straight Lines [id:da13747441694892726] 
    \draw    (155,171) -- (156,147) ;
    %Straight Lines [id:da4119117050779677] 
    \draw    (155,171) -- (176,187) ;
    %Straight Lines [id:da5379584617019675] 
    \draw    (221,169) -- (245,191) ;
    %Straight Lines [id:da788296500370655] 
    \draw    (245,191) -- (273,191) ;
    %Straight Lines [id:da4136462405421193] 
    \draw    (245,191) -- (222,209) ;
    %Straight Lines [id:da37414431568833373] 
    \draw    (273,191) -- (298,212) ;
    %Straight Lines [id:da8232480161298765] 
    \draw    (294,169) -- (273,191) ;
    %Straight Lines [id:da7983669347123197] 
    \draw    (294,169) -- (295,145) ;
    %Straight Lines [id:da7903324165137171] 
    \draw    (294,169) -- (315,185) ;

    % Text Node
    \draw (5,76.4) node [anchor=north west][inner sep=0.75pt]    {$m_{5}( I,I) =$};
    % Text Node
    \draw (87,114) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
    % Text Node
    \draw (86,68) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
    % Text Node
    \draw (159.5,56) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
    % Text Node
    \draw (180,84) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};
    % Text Node
    \draw (163,111) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
    % Text Node
    \draw (198,73.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
    % Text Node
    \draw (217,113) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
    % Text Node
    \draw (216,67) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
    % Text Node
    \draw (289.5,55) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};
    % Text Node
    \draw (310,83) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
    % Text Node
    \draw (293,110) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
    % Text Node
    \draw (335,72.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
    % Text Node
    \draw (362,107) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
    % Text Node
    \draw (361,61) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};
    % Text Node
    \draw (434.5,49) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
    % Text Node
    \draw (455,77) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
    % Text Node
    \draw (438,104) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
    % Text Node
    \draw (65,184.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
    % Text Node
    \draw (85,214) node [anchor=north west][inner sep=0.75pt]   [align=left] {4};
    % Text Node
    \draw (84,168) node [anchor=south west] [inner sep=0.75pt]   [align=left] {5};
    % Text Node
    \draw (157.5,156) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
    % Text Node
    \draw (178,184) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
    % Text Node
    \draw (161,211) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
    % Text Node
    \draw (201,181.4) node [anchor=north west][inner sep=0.75pt]    {$+$};
    % Text Node
    \draw (224,212) node [anchor=north west][inner sep=0.75pt]   [align=left] {5};
    % Text Node
    \draw (226,172) node [anchor=south west] [inner sep=0.75pt]   [align=left] {1};
    % Text Node
    \draw (296.5,154) node [anchor=south west] [inner sep=0.75pt]   [align=left] {2};
    % Text Node
    \draw (317,182) node [anchor=south west] [inner sep=0.75pt]   [align=left] {3};
    % Text Node
    \draw (300,209) node [anchor=south west] [inner sep=0.75pt]   [align=left] {4};

    \end{tikzpicture}
\end{frame}
\begin{frame}
    \frametitle{Trivalent graph expansion}
    \begin{alertblock}{Proposition}
        The function $m_n^{(0)}(\alpha|\beta)$ computes the sum of all trivalent scalar diagrams which can be regarded as both $\alpha$ color-ordered and $\beta$ color-orded.
    \end{alertblock}
    \pause
    More explictly, 
    \begin{equation*}
        \boxed{m_n^{(0)}(\alpha|\beta)=(-1)^{n-3+n_{\text{flip}}(\alpha|\beta)}\sum_{g\in\mathcal{T}(\alpha)\cap\mathcal{T}(\beta)}\prod_{e\in E(g)}\frac{1}{s_e}}
\end{equation*}
where the $\text{flip}(\alpha|\beta)$ is defined below, $\mathcal{T}(\alpha)$ and $\mathcal{T}(\beta)$ refer to the set of color-ordered diagrams in $\alpha$ and 
$\beta$ ordering respectively. To make this expression more clear, see the following diagram
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\linewidth]{5.png}
\end{figure}
\end{frame}
\begin{frame}
    We take $m_8^{(0)}(I;18543762)$ as an example to explain how to compute it in an systematic way
    \begin{itemize}
        \item First step, draw a disk with n nodes sitting on the boundary in the ordering $\alpha$, then link the n nodes with a loop of line segments according to
              the ording $\beta$. The line segments from $\beta$ split the disk into some polygons, like the graph (b). We need to move the external points of every polygon
              to make them have no common edges, like graph (c).
        \item Second step, put a point in every polygon, named equivalant vertex, and connect this point to all external points in corresponding area. Lines that connect equivalent 
              vertices in two regions with common vertices are called equivalent propagators. The resulting graph is an equivalent Feynman diagram, as shown in Figure (d).
    \end{itemize}
\end{frame}
\end{document}
